Instructions

### 2020-12-11 user-instructions/user-instructions.tex
updated user instructions

\section*{User input}

\subsubsection*{DOI}
DOI is the DOI access number of the simulation. Use the version DOI.

\subsubsection*{SYSTEM}
SYSTEM is name of the system.

@@

\subsubsection*{FF}
FF is the name of the forcefield used in the simulation.
\subsubsection*{FF\_SOURCE}
FF\_SOURCE tells where the forcefield parameters are taken from.
\subsubsection*{FF\_DATE}
FF\_DATE is the date when the forcefield parameters were created. The format is day/month/year.

\subsubsection*{TRJ}
TRJ stands for the name of the trajectory file.
\subsubsection*{TPR}
TPR stands for the name of the topology file.
\subsubsection*{PREEQTIME}
PREEQTIME means the time used for pre-equilibrating the system. This should be in nano seconds.
\subsubsection*{TIMELEFTOUT}
TIMELEFTOUT stands for the length of the simulation in nano seconds to be left out at the beginning of the simulation.
\subsubsection*{UNITEDATOM}
The handling of united atom simulations is enabled by a separate script called buildH\_calcOP.py. In case of a united atom simulation, the user has to give the names of the lipids and the corresponding names of those lipids as they are in the dic\_lipids.py dictionary used by buildH\_calcOP.py script. In case of an all atom simulation this can be given as an empty string.

\subsubsection*{Molecule names}
The user must also provide the names of the molecules, ions and solvent that are used. These are obtained from the tpr file. If a lipid consists of more than one residue the name of the head group residue is given.
\subsubsection*{dir\_wrk}
Finally the user has to give the path of the working directory.

>>>>

\subsection*{Compulsory user input}
The following parameters are compulsory and have a strict format.

\subsubsection*{DOI}
DOI is the DOI access number of the simulation. Use the version DOI on Zenodo.

@@

\subsubsection*{TRJ}
TRJ stands for the name of the trajectory file.
\subsubsection*{TPR}
TPR stands for the name of the topology file.

\subsubsection*{PREEQTIME}
PREEQTIME means the time used for pre-equilibrating the system. This should be in nano seconds. 
\subsubsection*{TIMELEFTOUT}
TIMELEFTOUT stands for the length of the simulation in nano seconds to be left out at the beginning of the simulation. This value is used in the script to leave out the given length from the analysis!

\subsubsection*{UNITEDATOM}
The handling of united atom simulations is enabled by a separate script called buildH\_calcOP.py. In case of a united atom simulation, the user has to give the names of the lipids and the corresponding names of those lipids as they are in the dic\_lipids.py dictionary used by buildH\_calcOP.py script. In case of an all atom simulation this can be given as an empty string.

\subsubsection*{Molecule names}
The databank has default names for lipids, ions and solvent. The user must also provide the names of the molecules, ions and solvent that are used in the simulation to match the names used by the databank. If the name of the molecule is not in the databank it needs to be added. The names provided by the user must be the same as in the tpr file. If a lipid consists of more than one residue the name of the head group residue is given.

\subsubsection*{dir\_wrk}
The user has to give the path of the working directory.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%free form parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Free form user input}
The form of how the values of these parameters are written is not essential for the script to work properly.
\subsubsection*{SYSTEM}
SYSTEM is name of the system.
\subsubsection*{FF}
FF is the name of the forcefield used in the simulation.
\subsubsection*{FF\_SOURCE}
FF\_SOURCE tells where the forcefield parameters are taken from.
\subsubsection*{FF\_DATE}
FF\_DATE is the date when the forcefield parameters were created. The format is day/month/year.

\subsection*{Automatically analyzed parameters}
The following parameters are read automatically from the trajectory and topology files.

\subsubsection*{Molecule numbers}
Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
\newline \\
\noindent Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file.

\subsubsection*{Temperature}
Temperature of the simulation is read from the topology file.

\subsubsection*{Trajectory length}
The length of a trajectory is read from the trajectory file.
